### 2025-06-21 docs/thesis/frontmatter/abstract.tex
Text improvements
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

Modern software systems are constantly evolving—requiring developers to
  refactor legacy code, adapt to changing APIs, translate across languages, and
  patch security vulnerabilities. These transformations are often brittle,
  manual, and error-prone. Large language models (LLMs) offer new opportunities
  for automating such tasks, but their outputs are shaped by surface cues, lack
  semantic guarantees, and require brittle prompting strategies. This paper
  presents \sys, a system for controllable program regeneration that combines
  logic-based planning with LLM-guided synthesis.
  By expressing transformation
  goals as declarative constraints over program properties---such as input/output
  behavior, side-effect freedom, language, or modular structure, \sys
  regenerates code that satisfies explicit semantic requirements.
  We demonstrate \sys across a wide range of tasks, including security
  hardening, language translation, and idiomatic rewriting, and highlight its
  ability to deliver interpretable, high-quality transformations with minimal
  developer guidance.

>>>>

Modern software systems are constantly evolving—requiring developers to
  refactor legacy code, adapt to changing APIs, translate across languages, and
  patch security vulnerabilities. These transformations are often brittle,
  manual, and error-prone. Large language models (LLMs) offer new opportunities
  for automating such tasks, but their outputs are shaped by surface cues, lack
  semantic guarantees, and require brittle prompting strategies. This paper
  presents \sys, a system for controllable program regeneration that combines
  logic-based planning with LLM-guided synthesis.

Kvasir operates in four stages: (1) a symbolic planner constructs a
transformation plan using logic rules and a domain-aware knowledge base; (2)
property extractors analyze the input program to gather relevant semantic
information; (3) a language model synthesizes candidate programs guided by
a structured prompt assembled from extracted properties; and (4) a verification
and feedback loop checks whether the output meets the desired properties and
iteratively refines the generation process through additional feedback.

\sys is evaluated on a diverse set of program transformation tasks
including security hardening, language translation, idiomatic rewriting, de-obfuscation,
and modular refactoring.
Target programs are sourced from high-profile supply-chain attacks, 
online repositories, programming competitions, and real-world software projects.
\sys produces high-quality outputs that satisfy goals in all but two cases,
even on instances where a state-of-the-art LLM fails to do so.

### 2025-06-21 docs/thesis/main.tex
Text improvements
Signed-off-by: Evangelos Lamprou <vagos@lamprou.xyz>

This paper present \sys, a system for \emph{controllable program regeneration}.
\sys allows users
to express transformation goals declaratively, as logical constraints over
program properties such as input/output behavior, side-effect freedom, target
language, trace equivalence, or modular structure.
As shown in \cref{fig:overview}, given a source program and
a query, \sys extracts a minimal set of relevant properties, guided by a
logic engine and a domain-specific knowledge base, and synthesizes a new
program that satisfies the desired constraints.

@@

\chapter{Example}
\label{sec:example}
\sys enables users to specify transformation goals declaratively.
Logical constraints over properties of the
regenerated program express these goals. Examples are input-output equivalence, side-effect elimination,
target language, lines of code, and others.

@@

This chapter shows the application of \sys
to three distinct program transformation tasks, 
targeting security, language translation, compatibility,
idiomaticity, and modularity.

@@

\begin{wrapfigure}[3]{r}{.5\columnwidth}
\vspace{-10pt}
\begin{minted}{prolog}
equal(graph(P), graph(P_)).
pure(P_).
\end{minted}
\end{wrapfigure}
To the right is a program written in the \sys DSL to express this intent.
This query requires the regenerated program \ttt{P\_} to exhibit the same I/O behavior,
but forbids side-effects.
\sys first arrives at a minimal set of properties to extract from the
original program, given its knowledge base and the query.
This set is $\{\texttt{funcs(F, P), graph(F), sig(F), pure(P)}\}$, where
\texttt{funcs(F, P)} extracts the set of functions defined in the original program
using a language-aware component that either parses the program source or extracts
symbols from the binary,
\texttt{graph(F)} extracts the I/O behavior of each function
by providing its source code to an LLM instance and asking it to generate a set of
inputs; with corresponding outputs generated by executing the original program,
and \texttt{sig(F)} extracts each function's signature.
The, \texttt{pure(P)} property means that \sys will confirm after regeneration that the original program is (obviously) pure
using static analysis.

@@

Having the database initialization being in the same function as 
the database access has architectural and performance implications.
In addition, there exist systems that can benefit from further decomposition
of an application towards automatic distribution, parallelization or security~\cite{Towards_Modern_Ghemaw_2023, vasilakis2019ignis, vasilakis2018breakapp}.
\begin{wrapfigure}[5]{r}{.7\columnwidth}
  \vspace{-10pt}
  \begin{minted}{prolog}
db('music.db').
equal(trace(P,sql),trace(P_,sql)).
func(F1). func(F2).
equal(F2(F1, _), P).
\end{minted}
\end{wrapfigure}
\sys, given the query to the right, will 
generate program that consists of two functions,
whose composition is equivalent to the original program, and feature 
the same I/O and trace properties (a trace here being the sequence of SQL 
queries transmitted to the database).
\sys wraps the node process with monitors that extract the SQL queries 
sent to the database for 24 generated inputs.
Then, after 20.4 seconds and two attempts, it arrives at two functions $f_1$, and 
$f_2$, where their composition $f_2(f_1, \_)$, is equivalent to the original \ttt{getAlbumsByArtist} function across these inputs.
A final processing step renames functions $f_1$ and $f_2$ by prompting an LLM instance.
Alternatively, the user could have provided specific signatures and names for each 
functions as an additional guiding property.
The resulting program is:
\begin{minted}[frame=lines]{js}
function connectDB() {
 const sqlite = require('sqlite');
 return sqlite.open({filename: 'music.db'}); }
function getAlbumsByArtist(db, artist) {
 const rows = await db.all("SELECT album
 FROM songs WHERE artist = ?", artist);
 return rows.map(row => row.album); }
\end{minted}

\heading{Key results}
\sys is able to effectively transform all programs across the above tasks,
producing high-quality outputs that satisfy user-specified constraints. A total
of six plugins were required to perform the above transformations, each
contributing either a set of extracted and verified properties, or a
transformation, and a set of pre- and post-conditions that the logic engine
uses to construct the regeneration plan.

\chapter{\sys Design}
\label{sec:design}

@@

\heading{Plan construction}
First, each of the available plugins contributes a set of pre and pos-conditions 
to the logic engine.
Essentially, these describe what needs to hold for an analysis to be applicable to the given 
program and what properties \sys will preserve or transform after regeneration.
Then, the planning component accepts one or more user-provided regeneration goals (termed as the query).
The full set of rules and predicates are used to construct an ASP program
a solver then accepts.
From the solver's output, the planner constructs a plan that specifies which
analysies \sys plugins should apply to the input program and what properties can be
preserved during regeneration in order to fullfill the query.

@@

\chapter{Property Language and Extraction}
\label{sec:dsl}

@@

\heading{Property predicates}
Each property is a logical predicate over the program symbol $p$. Common examples include:
\begin{itemize}
  \item \texttt{language}$(p, \texttt{javascript})$: the input program is written in JavaScript.
  \item \texttt{signature}$(p)$: the program exposes a well-formed function signature.
  \item \texttt{pure}$(p)$: the program does not have side-effects (\eg file system access, network calls, \etc).
\end{itemize}

Properties fall into three categories:
\begin{itemize}
  \item $\mathsf{goal}(X)$: the user requires $X$ to hold in the regenerated program. The system derives such facts from the user query.
  \item $\mathsf{can}(X)$: the system is capable of extracting or inferring property $X$ from the input. Plugins add these facts and represent the system's capabilities.
  \item $\mathsf{do}(X)$: $X$ the planner selects $X$ for enforcement and the synthesizer will preserve or regenerate it. 
\end{itemize}

\heading{Planning over properties}
The logic engine determines the set of active properties to enforce by solving a constrained optimization problem over $\mathsf{do}(\cdot)$. It satisfies the following constraints:
\begin{align*}
  \mathsf{goal}(X) &\Rightarrow \mathsf{do}(X) &\text{Satisfy all goals} \\
  \mathsf{do}(X) &\Leftarrow \mathsf{can}(X) &\text{Apply only extractable properties}
\end{align*}
\sys also supports minimization, maximization and elimination of properties
through the $\mathsf{goal\_min}$, $\mathsf{goal\_max}$, and $\mathsf{goal\_not}$ and the corresponding $\mathsf{do\_min}$, $\mathsf{do\_max}$, and $\mathsf{do\_not}$ predicates.
Without loss of generality, the text encompasses the four cases under $\mathsf{goal}$ and $\mathsf{do}$, explicitly mentioning the rest when there is an important semantic difference.

Additionally, the system maximizes the number of extracted properties:
\[
\text{maximize} \left|\left\{ X \mid \mathsf{do}(X) \right\}\right|
\]
Essentially, the planner tries to give the synthesizer as much information
as possible, as long as it doesn't violate any regeneration goals.

\heading{Plugin-defined rules}
Plugins contribute domain-specific inference rules and constraints. For example, a plugin for JavaScript-to-Haskell translation may define:
\begin{align*}
\mathsf{can}(\texttt{translate}_{\texttt{js} \rightarrow \texttt{hs}}(p)) & \\
\mathsf{do}(\texttt{translate}_{\texttt{js} \rightarrow \texttt{hs}}(p)) &\Rightarrow \mathsf{do}(\texttt{language}(p, \texttt{haskell})) \\
\mathsf{do}(\texttt{translate}_{\texttt{js} \rightarrow \texttt{hs}}(p)) &\Rightarrow \mathsf{language}(p, \texttt{javascript})
\end{align*}
Another plugin might contribute $\mathsf{can}(\texttt{signature}(p))$, indicating it can extract the function signature. At this stage, \sys only cares about semantics of each plugin in relation to how it might enable or violate 
other properties in the regenerated program.

\heading{Axioms and domain knowledge}
The logic engine also includes domain-wide axioms based on some common assumptions.
For example
$\mathsf{do}(\texttt{language}(p, \texttt{haskell})) \Rightarrow \mathsf{do}(\texttt{pure}(p))$
captures the assumption that programs written in Haskell are pure by default.
Such axioms allow inferred properties to trigger downstream constraints or synthesis behaviors.

@@

@@

\chapter{Synthesis Plan}
\label{sec:synthesis}

The synthesis process begins with a set of enforced properties $\{ X \mid \mathsf{do}(X) \}$
which the planner selected~(\cref{sec:dsl}).
These properties
reflect both user goals (\eg removing side effects, translating to a
different language) and structural characteristics of the input program that
the synthesizer will preserve.
The planner constructs a transformation plan that
specifies, for each relevant unit of code (typically a function), what
constraints must hold in the regenerated version.

For instance, a plan for regenerating a specific function $f$ might include:
\(\mathsf{do}(\texttt{language}(f, \texttt{haskell}))\) the function must be written in Haskell, 
\(\mathsf{do}(\texttt{pure}(f))\) the function must be side-effect-free, and 
\(\mathsf{do}(\texttt{signature}(f))\) the function must keep its signature.

@@

\chapter{Property Verification and Feedback Loop}
\label{sec:verification}

@@

\heading{Verification as property checking}
After synthesis, \sys invokes a set of property-specific checkers. Each checker is responsible for evaluating whether a property $X$ in $\mathsf{do}(X)$ holds for the regenerated program fragment. These checkers operate at varying levels of precision---ranging from structural pattern checks to light static or symbolic analysis---and are tailored to the property type.

Examples include:
\begin{itemize}
  \item For $\mathsf{do}(\texttt{no\_network}(f))$, the checker confirms the absence of known network APIs or imports.
  \item For $\mathsf{do}(\texttt{signature}(f))$, the checker matches the regenerated function's name, parameters, and arity against the extracted signature.
  \item For $\mathsf{do}(\texttt{pure}(f))$, the checker examines control flow and side-effecting operations to detect possible violations.
\end{itemize}

@@

\begin{table}[h]
\centering
  \caption{\textbf{Benchmark summary}. 
  Benchmark programs come from online repositories, public archives, security research datasets, and often referenced examples in programming culture.
  The N column shows the number of programs/functions from each benchmar.
  }
\begin{tabular}{llrl}
\toprule
Benchmark                          & Description         & N & Source \\
\midrule
Rosetta Code                       & Programming tasks   & 16   & \cite{rosettacode} \\
npm utilities                      & Utilities from npm  & 10  & \cite{regbench2025} \\
PyPi utilities                   & Utilities from PyPi & 3   & \cite{regbench2025} \\
SSCA                               & Sneaky SSAs         & 3   & \cite{ev:eurosec:2022, ohm2020backstabber,copeland2019frightening} \\
IOCCC                              & Obfuscated C code   & 2   & \cite{ioccc} \\
Microbenchmarks                    &                     & 3   & \\
\hspace{.5em} \ttt{flatmap-stream} & Secure regeneration &     & \cite{es1}  \\
\hspace{.5em} \ttt{Q\_rsqrt}       & C refactoring       &     & \cite{fast_inv_sqrt}  \\
\hspace{.5em} \textsf{rigidDB}     & Modularization      &     & \cite{codewithsadeemusicplayer} \\
\bottomrule
\end{tabular}
\label{tab:benchmarks}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{Correctness: Percentage of tasks passing all tests (when present) and manual inspection.}
  \begin{tabular}{lc}
    \toprule
    Benchmark & \sys Pass Rate \\ 
    \midrule
    Rosetta Code & 16/16  \\
    npm Utilities & 10/10 \\
    Python Utilities & 3/3\\
    SSCA & 3/3  \\
    IOCCC & 1/2 \\
    Microbenchmarks & 2.5/3  \\
    \bottomrule
  \end{tabular}
\end{table}

>>>>

This paper present \sys, a system for \emph{property-guided program regeneration}.
\sys allows users
to express transformation goals declaratively, as logical constraints over
program properties such as input/output behavior, side-effect freedom, target
language, trace equivalence, or modular structure.
As shown in \cref{fig:overview}, given a source program and
a query, \sys extracts a minimal set of relevant properties, guided by a
logic engine and a domain-specific knowledge base, and synthesizes a new
program that satisfies the desired constraints.

@@

\chapter{\sys Implementation}

\sys enables users to specify transformation goals declaratively.
Logical constraints over properties of the
regenerated program express these goals. Examples are input-output equivalence, side-effect elimination,
target language, lines of code, and others.

@@

\section{Example}
\label{sec:example}
This chapter shows the application of \sys
to three distinct program transformation tasks, 
targeting security, language translation, compatibility,
idiomaticity, and modularity.

@@

\begin{wrapfigure}[3]{r}{.5\columnwidth}
\vspace{-10pt}
\begin{minted}{prolog}
graph(P_, I, O) :- graph(P, I, O).
:- not pure(P_).
\end{minted}
\end{wrapfigure}
To the right is a program written in the \sys DSL to express this intent.
This query requires the regenerated program \ttt{P\_} to exhibit the same I/O behavior,
but forbids side-effects.
\sys first arrives at a minimal set of properties to extract from the
original program, given its knowledge base and the query.
This set is $\{\texttt{input(P, I), graph(P, I, O), signature(P, S), pure(P)}\}$, where
\texttt{input(P, I)} means that \sys will use the \ttt{input} plugin extract a set of inputs from the original program
by providing the program's source code to an LLM instance and asking it to generate a set of inputs;
\texttt{graph(P, I, O)} extracts the client-observable I/O behavior of the program
by executing the original program on the generated inputs and recording the outputs;
and \texttt{signature(P, S)} extracts each function's signature using a language-aware parser.
The, \texttt{pure(P)} property means that \sys will not provide to the LLM 
instance any information that could encode side-effects, such as the
program's source code, a system call trace, or a filesystem access trace.

@@

Having the database initialization being in the same function as 
the database access has architectural and performance implications.
In addition, there exist systems that can benefit from further decomposition
of an application towards automatic distribution, parallelization or security~\cite{Towards_Modern_Ghemaw_2023, vasilakis2019ignis, vasilakis2018breakapp}.
\begin{wrapfigure}[5]{r}{.7\columnwidth}
  \vspace{-10pt}
  \begin{minted}{prolog}
db('music.db').
trace_sql(p_, T) :- trace_sql(p, T).
func(f1). func(f2).
graph(call(f2, call(f1), I), I, O) :- graph(p, I, O).
\end{minted}
\end{wrapfigure}
\sys, given the query to the right, will 
generate program that consists of two functions,
whose composition is equivalent to the original program, and feature 
the same I/O and trace properties (a trace here being the sequence of SQL 
queries transmitted to the database) driven by an input.
\sys wraps the node process with monitors that extract the SQL queries 
sent to the database for 24 generated inputs.
Then, after 20.4 seconds and two attempts, it arrives at two functions $f_1$, and 
$f_2$, where their composition $f_2(f_1(), i)$,
is equivalent to the original \ttt{getAlbumsByArtist} function across each input $i$.
A final processing step renames functions $f_1$ and $f_2$ by prompting an LLM instance.
Alternatively, the user could have provided specific signatures and names for each 
functions as an additional guiding property.
The resulting program is:
\begin{minted}[frame=lines]{js}
function connectDB() {
 const sqlite = require('sqlite');
 return sqlite.open({filename: 'music.db'});
}

function getAlbumsByArtist(db, artist) {
 const rows = await db.all("SELECT album
 FROM songs WHERE artist = ?", artist);
 return rows.map(row => row.album); 
}
\end{minted}

\heading{Key results}
\sys is able to effectively transform all programs across the above tasks,
producing high-quality outputs that satisfy user-specified constraints.
A total
of six plugins (\ttt{input}, \ttt{graph}, \ttt{signature}, \ttt{pure}, \ttt{trace\_sql}, and \ttt{javascript2haskell})
were required to perform the above transformations, each
contributing either a set of extracted and verified properties, or a
transformation, and a set of pre- and post-conditions that the logic engine
uses to construct the regeneration plan.

\section{Overall Design}
\label{sec:design}

@@

\heading{Plan construction}
First, each of the available plugins contributes a set of pre and pos-conditions 
to the logic engine.
Essentially, these describe what needs to hold for an analysis to be applicable to the given 
program and what properties \sys will preserve or transform after regeneration.
Then, the planning component accepts one or more user-provided regeneration goals (termed as the query).
The full set of rules and predicates are used to construct an ASP program
which is then given to an off-the-shelf solver~\cite{gebser2007clasp}.
% TODO: Explain what the solvr does (optimization)
From the solver's output, the planner constructs a plan that specifies which
analysies \sys plugins should apply to the input program and what properties can be
preserved during regeneration in order to fullfill the query.

@@

\section{Property Language and Extraction}
\label{sec:dsl}

@@

\heading{Property predicates}
Each property is a logical predicate over the program symbol $p$. Examples include:
\begin{itemize}
  \item \texttt{language}$(p, \texttt{javascript})$: the input program is written in JavaScript.
  \item \texttt{signature}$(p, S)$: the program exposes a well-formed function signature $S$.
  \item \texttt{pure}$(p)$: the program does not have side-effects (\eg file system access, network calls, \etc).
\end{itemize}

A property $X$ appears as either an
  $\mathsf{can}(X)$ atom, which denotes that the system is capable of extracting or inferring property $X$ from the input.
  Plugins add these facts and represent the system's capabilities.
  a pure $X$ atom, which denotes that either the user has explicitly requested property $X$ to be enforced, or the planner has deduced that it is necessary to satisfy the query.

\heading{Planning over properties}
The logic engine determines the set of active properties to enforce by solving
a constrained optimization problem over the property set $P_r$.
It satisfies the
following key contraint:
\begin{align*}
  X &\Leftarrow \mathsf{can}(X) &\text{Apply only extractable properties}
\end{align*}
\sys also supports minimization, maximization and elimination of properties
through the $\mathsf{min}$, $\mathsf{max}$, and $\mathsf{not}$ directives.
Without loss of generality, the base case is described, explicitly mentioning any significant semantic difference when necessary.

Additionally, the system minimizes the number of extracted properties:
\[
\text{minimize} \left|\left\{ X \mid \mathsf{can}(X) \right\}\right|
\]
Essentially, the planner tries to give the synthesizer the least amount of information
possible, as long as all regeneration goals are fulfilled.

\heading{Plugin-defined rules}
Plugins contribute domain-specific inference rules and constraints. For example, a plugin for JavaScript-to-Haskell translation may define:
\begin{align*}
\mathsf{can}(\texttt{translate}_{\texttt{js} \rightarrow \texttt{hs}}(p)) & \\
\texttt{translate}_{\texttt{js} \rightarrow \texttt{hs}}(p) &\Rightarrow \texttt{language}(p, \texttt{haskell}) \\
\texttt{translate}_{\texttt{js} \rightarrow \texttt{hs}}(p) &\Rightarrow \mathsf{language}(p, \texttt{javascript})
\end{align*}
Another plugin might contribute $\mathsf{can}(\texttt{signature}(p))$, indicating it can extract the function signature. At this stage, \sys only cares about semantics of each plugin in relation to how it might enable or violate 
other properties in the regenerated program.

\heading{Axioms and domain knowledge}
The logic engine also includes domain-wide axioms based on some common assumptions.
For example
$\texttt{language}(p, \texttt{haskell}) \Rightarrow \texttt{pure}(p)$
captures the assumption that programs written in Haskell are pure by default.
Such axioms allow inferred properties to trigger downstream constraints or synthesis behaviors.

@@

\heading{Abstract and concrete space}
% TODO: Show graph showing how properties go from the abstract logic domain to the real domain through a translation barrier

@@

\section{Synthesis Plan}
\label{sec:synthesis}

The synthesis process begins with a set of enforced properties $\mathbf{X}$
which the planner selected~(\cref{sec:dsl}).
These properties
reflect both user goals (\eg removing side effects, translating to a
different language) and structural characteristics of the input program that
the synthesizer will preserve.
The planner constructs a transformation plan that
specifies, for each relevant unit of code (typically a function), what
constraints must hold in the regenerated version.

For instance, a plan for regenerating a specific function $f$ might include:
\texttt{language}(f, \texttt{haskell}) the function must be written in Haskell, 
\texttt{pure}(f)) the function must be side-effect-free, and 
\texttt{signature}(f, s)) the function must keep the original program's signature $s$.

@@

\section{Property Verification and Feedback Loop}
\label{sec:verification}

@@

\heading{Verification as property checking}
After synthesis, \sys invokes a set of property-specific checkers.
Each checker
is responsible for evaluating whether a property $X$ holds
for the regenerated program fragment.
These checkers operate at varying levels
of precision---ranging from structural pattern checks to light static or
symbolic analysis---and are tailored to the property type.

Examples include:
\begin{itemize}
  \item For $\texttt{no\_network}(f)$, the checker confirms the absence of known network APIs or imports.
  \item For $\texttt{signature}(f)$, the checker matches the regenerated function's name, parameters, and arity against the extracted signature.
  \item For $\texttt{pure}(f)$, the checker examines control flow and side-effecting operations to detect possible violations.
\end{itemize}

@@

\begin{table}[h]
\centering
  \caption{\textbf{Benchmark summary}. 
  Benchmark programs come from online repositories, public archives, security research datasets, and often referenced examples in programming culture.
The N column shows the number of programs/functions from each benchmar.
}
\begin{tabular}{llrll}
\toprule
Benchmark                          & Description         & N  & Task                                       & Source \\
\midrule
Rosetta Code                       & Programming tasks   & 16 & Language translation                       & \cite{rosettacode} \\
Short utilities                    & npm and Pypi utilities & 13 & Pure and idiomatic regeneration    & \cite{regbench2025} \\
SSCA                               & Sneaky SSAs         & 3  & Malicious code elimination                 & \cite{ev:eurosec:2022, ohm2020backstabber,copeland2019frightening} \\
IOCCC                              & Obfuscated C code   & 2  & De-obfuscation                             & \cite{ioccc} \\
Microbenchmarks                    &                     & 3  &                                            & \\
\hspace{.5em} \ttt{flatmap-stream} & Secure regeneration &    & Pure regeneration and translation & \cite{es1}  \\
\hspace{.5em} \ttt{Q\_rsqrt}       & C refactoring       &    & Idiomatic rewrite                          & \cite{fast_inv_sqrt}  \\
\hspace{.5em} \textsf{rigidDB}     & Modularization      &    & Modularization                             & \cite{codewithsadeemusicplayer} \\
\bottomrule
\end{tabular}
\label{tab:benchmarks}
\end{table}

@@

\begin{table}[h]
  \centering
  \caption{Correctness: Percentage of tasks passing all tests (when present) and manual inspection.}
  \begin{tabular}{lc}
    \toprule
    Benchmark & \sys Pass Rate \\ 
    \midrule
    Rosetta Code & 16/16  \\
    Short Utilities & 13/10 \\
    SSCA & 3/3  \\
    IOCCC & 1/2 \\
    Microbenchmarks & 2.5/3  \\
    \bottomrule
  \end{tabular}
\end{table}
